---
title: "rpackages"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{rpackages}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(rpackages)
```

# Package Description

The goal of rpackages is to complete Coursera’s assignment for building R packages.


# Load Packages

```{r}
library(rpackages)
```

# Included Data

Data files located in:

```{r}
list.files(system.file('extdata'), package = 'rpackages')
```

## Package Functions

### Function 'make_filename'

Returns a filename with the prefix 'accident_' followed by a given year

```{r}
make_filename(2015)
```

### Function 'fars_read_years'

Reads the accident data for given year(s), and return the year and month of the found observations

```{r}
fars_read_years(2013)
```

### Function 'fars_summarize_years'

Summarizes yearly accident data, by month and year

```{r}
plot(fars_summarize_years(2015))
fars_summarize_years(c(2015, 2014))
```

### Function 'fars_map_state'

Displays a map plotting the location of accidents in a certain state for a certain year

```{r}
fars_map_state(49, 2014)